Enhancement of SDR in Thessaloniki

### 2024-07-05 GHI_enh_04_investigate.tex
Commit 2024-07-05 13:12

@@

\caption{ - empty caption - }\label{fig:groups-9}
\end{figure}

@@

\caption{ - empty caption - }\label{fig:groups-12}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-13}
\end{figure}

@@

\caption{ - empty caption - }\label{fig:groups-14}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-15}

\caption{ - empty caption - }\label{fig:groups-15}
\end{figure}

@@

\begin{verbatim}
2024-07-05 08:41:25.9 athan@tyler GHI_enh_04_investigate.R 1.700820 mins
\end{verbatim}

>>>>

\begin{verbatim}
Attaching package: 'ggpubr'
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:cowplot':

    get_legend
\end{verbatim}

\begin{verbatim}
The following objects are masked from 'package:ggpp':

    as_npc, as_npcx, as_npcy
\end{verbatim}

@@

\caption{ - empty caption - }\label{fig:groups-9}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-12}
\end{figure}

@@

\caption{ - empty caption - }\label{fig:groups-13}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-14}
\end{figure}

@@

\begin{verbatim}
2024-07-05 09:30:57.8 athan@tyler GHI_enh_04_investigate.R 2.177551 mins
\end{verbatim}
